Automated detection \& characterization of long-period transits in the \kepler\ archive

### 2016-01-04 document/ms.tex
adding a figure

@@

\begin{figure}[p]
\begin{center}
\includegraphics{figures/predict.pdf}
\end{center}
\caption{%
The expected number of single transit events---extrapolated from the
\citet{Dong:2013} power-law model fit to the shorter period \kepler\
candidates---as a function of the effective signal-to-noise threshold of the
search procedure.
The shaded region indicates the uncertainties propagated from the model
parameters.
\figlabel{predict}}
\end{figure}

>>>>

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/model_comp.pdf}
\end{center}
\caption{%
Model comparison.
\figlabel{model-comp}}
\end{figure}

@@
